\begin{frame}
  \frametitle{Conclusions}
        \begin{block}{This study outcomes}
        \begin{itemize}
                \item \gls{MSBR} unit cell online reprocessing simulation was performed using the SERPENT 2 Monte Carlo code to find equilibrium fuel composition.
                \item Infinite multiplication factor slowly decreases and reaches to the equilibrium state after 950 days of operation.
                \item To achieve equilibrium state and maintain criticality material flow rate should be adjusted, ideally, for each 3-day step.
                \item The neutron energy spectrum is harder for equilibrium state because significant amount of heavy fission products were accumulated in the \gls{MSBR} core.
        \end{itemize}
        \end{block}
        
\end{frame}

\begin{frame}
  \frametitle{Future research}
         
              \begin{block}{Future research effort}
                 \begin{enumerate}
                \item Depletion simulation using a full-core, 3-D, high-fidelity MSBR model.
                \item Additional SERPENT 2 flow control system development to simulate adjusting material flows depending upon the instantaneous reactivity value.
                \item Reprocessing parameters (e.g. time step, feeding rate, protactinium removal rate) optimization will be performed to achieve maximum fuel utilization, breeding ratio or minimize amount of wastes.
                \item Temperature coefficients of reactivity, rod worth, power density will be computed for initial and equlibrium fuel composition to determine influence of fuel depletion on \gls{MSBR} safety.
               \end{enumerate}
               \end{block}
\end{frame}
